\textbf{ Spectrophotometric parallaxes with \project{The Cygnet}:\\ Accurate distances for luminous red-giant stars }

### 2018-08-03 paper/sp.tex
symbols

% math macros
\newcommand{\T}{^{\mathsf{T}}}
\DeclareMathOperator*{\argmin}{argmin}
\newcommand{\logg}{\log g}
\newcommand{\gparallax}{\varpi^{(\mathrm{a})}}
\newcommand{\sparallax}{\varpi^{(\mathrm{sp})}}

@@

Our position is that a methodological technique is correct inasmuch as
it delivers correct or best results \emph{under its particular assumptions}.
In that spirit, we present here the assumptions of the method
explicitly.
We will return to these assumptions in the Discussion section below,
to address the costs and benefits of each in more depth.
\begin{description}
\item[features] Perhaps our most fundamental assumption is that the parallax
of a star can be predicted from the features we provide, which are
the full set of (pseudo-continuum-normalized) pixels from the \apogee\ spectrum,
plus the $G$ and $({BP}-{RP})$ photometry from \gaia,
plus the $J$, $H$, and $K_s$ photometry from \zmass (\citealt{zmass}),
plus the $W_1$ and $W_2$ photometry from \wise.
That is, we assume that these spectrophotometric \emph{features} are sufficient
to predict the parallax in the face of variations in stellar
age, evolutionary phase, composition, and other parameters, and also interstellar
extinction.

@@

We match this full-match catalog to the \gaia\ \acronym{DR2} (HOGG CITE)
using the \gaia\ Archive official match (given the \zmass\ IDs).
We take from the \gaia\ \acronym{DR2} Catalog the photometric data
$G_n$ (\code{phot_g_mean_mag}),
${BP}_n$ (\code{phot_bp_mean_mag}),
and ${RP}_n$ (\code{phot_rp_mean_mag}),
which will become part of the feature vector $x_n$.

We need complete feature-vector information for all stars.  For this
reason, we define the Parent Sample to be the set of all stars that
meet the \apogee\ and \gaia\ cuts and also
have the complete set of photometry: $G_n$, ${BP}_n$, ${RP}_n$, $J_n$,
$H_n$, $K_n$, $W_{1n}$, and $W_{2n}$ and also an apogee spectrum.
This Parent Sample contains ACE HOW MANY STARS? and is shown in HOGG WHAT FIGURES?

@@

For every star $n$ in the full Parent Sample we construct the feature
vector $x_n$ as
\begin{eqnarray}
x_n\T &\equiv& [1, G_n, {BP}_n, {RP}_n, J_n, H_n, K_n, W_{1n}, W_{2n}, \ln f_{1n}, \ln f_{2n}, \cdots, \ln f_{Ln}]
\quad ,
\end{eqnarray}
where the 1 permits a linear offset,
the photometry is from \gaia, \zmass, and \wise, respectively,
the fluxes in the $L=7405$ \apogee\ spectral pixels (for which there are reliably
and consistently data) for star $n$ are denoted
$f_{1n}$, $f_{2n}$, and so on,
and we have taken logarithms of those fluxes.
These feature vectors live in a $D$-dimensional space where $D=7414$
For every star $n$ in either of the Training Sets we additionally require---in
addition to these feature vectors---a \gaia-measured parallax $\gparallax_n$
and uncertainty $\sigma_n$.

>>>>

% math macros
\newcommand{\T}{^{\mathsf{T}}}
\DeclareMathOperator*{\argmin}{argmin}
\newcommand{\logg}{\log g}
\newcommand{\BP}{B\!P}
\newcommand{\RP}{R\!P}
\newcommand{\gparallax}{\varpi^{(\mathrm{a})}}
\newcommand{\sparallax}{\varpi^{(\mathrm{sp})}}

@@

Our position is that a methodological technique is correct inasmuch as
it delivers correct or best results \emph{under its particular assumptions}.
In that spirit, we present here the assumptions of the method
explicitly.
We will return to these assumptions in the Discussion section below,
to address the costs and benefits of each in more depth.
\begin{description}
\item[features] Perhaps our most fundamental assumption is that the parallax
of a star can be predicted from the features we provide, which are
the full set of (pseudo-continuum-normalized) pixels from the \apogee\ spectrum,
plus the $G$ and $(\BP-\RP)$ photometry from \gaia,
plus the $J$, $H$, and $K_s$ photometry from \zmass (\citealt{zmass}),
plus the $W_1$ and $W_2$ photometry from \wise.
That is, we assume that these spectrophotometric \emph{features} are sufficient
to predict the parallax in the face of variations in stellar
age, evolutionary phase, composition, and other parameters, and also interstellar
extinction.

@@

We match this full-match catalog to the \gaia\ \acronym{DR2} (HOGG CITE)
using the \gaia\ Archive official match (given the \zmass\ IDs).
We take from the \gaia\ \acronym{DR2} Catalog the photometric data
$G_n$ (\code{phot_g_mean_mag}),
$\BP_n$ (\code{phot_bp_mean_mag}),
and $\RP_n$ (\code{phot_rp_mean_mag}),
which will become part of the feature vector $x_n$.

We need complete feature-vector information for all stars.  For this
reason, we define the Parent Sample to be the set of all stars that
meet the \apogee\ and \gaia\ cuts and also
have the complete set of photometry: $G_n$, $\BP_n$, $\RP_n$, $J_n$,
$H_n$, $K_n$, $W_{1n}$, and $W_{2n}$ and also an apogee spectrum.
This Parent Sample contains ACE HOW MANY STARS? and is shown in HOGG WHAT FIGURES?

@@

For every star $n$ in the full Parent Sample we construct the feature
vector $x_n$ as
\begin{eqnarray}
x_n\T &\equiv& [1, G_n, \BP_n, \RP_n, J_n, H_n, K_n, W_{1n}, W_{2n}, \ln f_{1n}, \ln f_{2n}, \cdots, \ln f_{Ln}]
\quad ,
\end{eqnarray}
where the 1 permits a linear offset,
the photometry is from \gaia, \zmass, and \wise, respectively,
the fluxes in the $L=7405$ \apogee\ spectral pixels (for which there are reliably
and consistently data) for star $n$ are denoted
$f_{1n}$, $f_{2n}$, and so on,
and we have taken logarithms of those fluxes.
These feature vectors live in a $D$-dimensional space where $D=7414$
For every star $n$ in either of the Training Sets we additionally require---in
addition to these feature vectors---a \gaia-measured parallax $\gparallax_n$
and uncertainty $\sigma_n$.
